Water, High-Altitude Condensates, and No Methane in the Atmosphere of the Warm Neptune WASP-107b

### 2017-07-04 ms.tex
spec lc

\author{Laura Kreidberg}
\affiliation{Harvard Society of Fellows\
78 Mt. Auburn St.\\
Cambridge, MA 02138, USA}
\affiliation{Harvard-Smithsonian Center for Astrophysics\
60 Garden St.\\
Cambridge, MA 02138}
\nocollaboration

@@

\subsection{White Light Curve Fit}
To create the raw white light curve, we summed each spectrum over the FIXME pixels in the spectral trace.  The morphology of the white light curve is typical for WFC3 observations \cite{zhou17}: the flux increases increases asymptotically over each orbit (the ``ramp" effect) and there is a visit-long linear trend. The largest ramp occurs in the initial orbit (orbit zero), so we only fit data from orbits one through four in our analysis, following common practice.

We fit the light curve with the analytic model of the form $F(t) = S(t)\times T(t)$, where $S$ is a systematics model and $T$ is a transit model. We used the same systematics model as FIXME, equation FIXME.  To model the transit, we used the \texttt{batman} package \citep{kreidberg15b}.  In our initial fit, we noticed an increase in flux during orbit three. We also found . We gave the data in orbit three no weight in the fit, and found that the

In our final fit, we fixed the transit parameters on the values from \cite{dai17}.

fixed LD on PHOENIX model

\subsection{Spectroscopic Light Curve Fits}
We explored two different methods for fitting the spectroscopic light curves.

@@

\begin{equation}
x
\end{equation}

Star Spots?

Confirmation from KBS

>>>>

\author{Laura Kreidberg, Michael Line}
\affiliation{Harvard Society of Fellows\
78 Mt. Auburn St.\\
Cambridge, MA 02138, USA}
\affiliation{Harvard-Smithsonian Center for Astrophysics\
60 Garden St.\\
Cambridge, MA 02138}
\nocollaboration

@@

\subsection{White Light Curve Fit}
To create the raw white light curve, we summed each spectrum over the FIXME pixels in the spectral trace.  The white light curve has systematic trends that are typical for WFC3 observations \cite{zhou17}: the flux increases increases asymptotically over each orbit (the ``ramp" effect) and there is a visit-long linear trend. The largest ramp occurs in the initial orbit (orbit zero), so we only fit data from orbits one through four in our analysis, following common practice.  We fit the light curve with the analytic model of the form $F_\mathrm{white}(t) = S_\mathrm{white}(t)\times T_\mathrm{white}(t)$, where $S$ is a systematics model and $T$ is a transit model. We used the same systematics model as FIXME, equation FIXME.  To model the transit, we used the \texttt{batman} package \citep{kreidberg15b}.  The transit model parameters are the orbital period $p$, time of FIXME $t_c$, transit depth $r_p/r_s$, ratio of semi-major axis to stellar radius $a/r_s$, orbital inclination $i$, and the quadratic stellar limb darkening parameters $u_1$ and $u_2$.

\subsubsection{Star Spot Crossing}
In our initial fit, we allowed all the transit parameters to vary freely. We noticed two odd results: first, there was a slight increase in flux during orbit three, and second, the transit parameters were inconsistent with the precise analysis of the Kepler light curve from \cite{dai17}.  We conjectured that the anomalies could be due to a star-spot crossing event in orbit three, as WASP-107 is an active star and spot crossings have been observed before FIXME. To test this idea, we gave the data in orbit three no weight in the fit. For this case, the transit parameters agree well with those of \cite{dai17} and the spot-crossing feature is more pronounced (see Figure FIXME). The amplitude of the feature is FIXME ppm, consistent with a spot of FIXME size and temperature (cf dai17 FIXME).  We conclude that the feature is indeed due to a spot crossing.

\subsubsection{Final Fit}
In our final fit, we fixed the transit parameters $a/r_s$, $i$, $p$ on the values from \cite{dai17}.  We also fixed the limb darkening parameters on predictions from a PHOENIX model for a star of FIXME properties, calculated with the FIXME package.  The model values are consistent with what we obtain from fitting for the limb darkening coefficients as free parameters. The remaining free parameters were $t_c$, $r_p/r_s$, and the systematics parameters for the visit-long and orbit-long trends.

For the best fit light curve, the root-mean-square residuals were FIXME ppm (not including orbit three), compared to the expected shot noise of FIXME ppm. The achieved rms is close to the best value obtained for WFC3 data (FIXME), and we attribute the slight excess noise to either additional star spot crossings or loss of flux from the edge of the detector \citep[as has been seen for other bright targets;][]{FIXME}. We used the Markov chain Monte Carlo algorithm to estimate parameter uncertainties (as implemented in the the \texttt{emcee} package; FIXME). We scaled the per-point uncertainties by a factor of FIXME to achieve a reduced $\chi_2$ value of unity. The transit time was FIXME and the planet/star radius was FIXME.

\subsection{Spectroscopic Light Curve Fits}
We binned the spectrum into 20 spectrophotometric channels from FIXME to FIXME $\mu$m, shown in Figure FIXME. We fit the light curves with the \texttt{divide-white} technique, which assumes that the light curve systematics are nearly constant as a function of wavelength \citep{stevenson??, kreidberg14a}. For this method, the transit model $T_\lambda(t)$ is multiplied by the systematics vector from the white light curve fit ($F_\mathrm{white}/T_\mathrm{white}$), and rescaled by a factor $C_\lambda + V_\lambda t$.  An advantage of this approach is that it removes the star spot crossing feature, enabling us to use orbit three with no additional correction. There is a small chromatic effect due to the changing amplitude of the spot crossing feature with wavelength, but this effect is below the level of noise in our data FIXME.  As for the white light curve, we fixed some of the transit parameters on the estimates from \cite{dai17} and fixed the limb darkening on the PHOENIX model. The fit has just three free parameters: $C_\lambda$, $V_\lambda$, and $r_p/r_s$.

The best fit light curves have a median reduced $\chi_2$ value of FIXME and rms values consistent with the expected photon shot noise.  There are two channels with slightly higher $\chi_2$ values: FIXME and FIXME. We therefore rescale the photometric uncertainties for all spectroscopic channels such that the $\chi_2$ values are unity, to ensure that we do not underestimate the uncertainty on the transit depths. We performed an MCMC fit to the light curves with \texttt{emcee}. The median transit depths and $1\,\sigma$ uncertainties are given in Table FIXME. FIXME: does the  median agree with the best fit? FIXME: convergence?

We explored several alternative choices for the spectroscopic light curve fits, but found that none of them made a significant difference in the transmission spectrum. We tested fitting the spectroscopic light curves with the same analytic model we used for the white light curve and obtained nearly identical relative transit depths (FIXME sigma), except offset by a constant value of FIXME ppm. We attribute the offset to the uncorrected star-spot crossing feature. Regardless of the cause, the offset does not affect our final analysis, because the planet's 1 bar radius is a free parameter in the atmospheric retrieval (see \S FIXME). We also explored fitting for a linear limb darkening parameter rather than fixing the limb darkening on the PHOENIX model predictions, and found that the `fitted limb darkening coefficients are consistent with the model.  We opted to fix the coefficients in our final analysis because the uncertainties on the transit depths are slightly smaller (about 10\%). We also checked whether the uncertainty in the stellar parameters significantly affects the PHOENIX model predictions, and found that changing the stellar

\subsubsection{Transit Depths Redder than FIXME $\mu$m}
The red edge of the transmission spectrum is of interest for our analysis because methane becomes the dominant absorber over water at wavelengths $> 1.6\,\mu$m. Unfortunately, we find that the spectroscopic light curves between FIXME $\mu$m are too poor in quality to accurately measure the transit depth. The residuals show evidence for correlated noise and the reduced $\chi_2$ values increase to FIXME.

@@
